Factor Analysis on Report Citations, using a Combined Latent and logistic Model

### 2019-05-16 Manuscript for submission/manuscript.tex
latex work
latex work 3

\author[1]{Namjoon Suh*}

\author[1]{Xiaoming Huo}

\author[2]{Eric Heim}

\author[2]{Timothy Van Slyke}

\author[2]{Lee Seversky}

@@

\jnlcitation{\cname{%
\author{Williams K.},
\author{B. Hoskins},
\author{R. Lee},
\author{G. Masato}, and
\author{T. Woollings}} (\cyear{2016}),
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

@@

\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

@@

\item To ensure unique separation of $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad where \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T
\]
This condition uniquely identifies F up to a common orthogonal transformation of its columns.

@@

We propose a penalize likelihood estimation approach as follows:
\begin{eqnarray}
\label{eq:logistic10}
(\hat{\alpha}, \hat{L}, \hat{S})
= \mbox{arg min}_{\alpha, L, S} \left\{
-\frac{1}{n} \mathbb{L}_n(\alpha,  L, S; X) + \gamma \|S\|_1
+ \delta \|L\|_\ast\right\},
\end{eqnarray}
where $\gamma>0$ and $\delta>0$ are algorithmic parameters whose values will be discussed later,
the $L_1$ norm of matrix $S$ is defined as $\|S\|_1 = \sum_{i\neq j} S_{ij}$ (Note that we do not penalize the diagonal entries of $S$), and nuclear norm of matrix $L$ is defined as $\|L\|_\ast = {\mbox{trace}\sqrt{(L^T L)}}$. 
Recall that both $S$ and $L$ are symmetric matrices. 
The entries of matrix $S$ can either be positive or negative. 
Note that we have imposed the diagonal entries of the matrix $X$ to be zeros. 
Given that $L = F^T D F$ where matrix $D$ is diagonal with nonnegative diagonal entries, it is easy to see that matrix $L$ is positive semidefinite; which consequently leads to $\|L\|_\ast = \mbox{trace}(L)$, which is a linear functional to the matrix $L$.
The nuclear norm of $L$ penalizes the number of nonzero eigenvalues of $L$, which is the same as the rank
of $L$.
The regularization based on the nuclear norm was proposed in \cite{fazel2001rank}
and its statistical properties are studied in \cite{bach2008consistency}.

After we have obtained $\hat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\hat{S}$.
On the other hand when we have calculated $\hat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\hat{L} = F^T D F.$
This is the price we have to pay for an amenable computational problem. 
The rank of estimated $\hat{L}$ will be our estimate of the number of factors (i.e., underlying common topics). 
For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.

@@

\subsection{Synthetic data}
\textbf{Data Generation} Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
\alpha+F_{i}^{T}DF_{j} +  S_{ij})}{1+\exp(\alpha+F_{i}^{T}DF_{j}+S_{ij})}$. 
For sparse component $S$, we generate random numbers uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S$, and make it symmetry. 
$F^{T}$ binary matrix has $\floor{\frac{n}{K}}$ ones in each columns, and has exactly one 1 in each rows.
We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying $I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$. 
Diagonal elements of $D$ are generated from $unif[7,8]$, and alpha is generated from $unif[-3,-2]$. 
We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of upper-triangular part of S.\\

\noindent \textbf{Choosing tuning parameter}
We have to admit the fact that choosing good tuning parameter is an important but challenging issue in our problem.
In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size "n", when we have n i.i.d. observations. 
Our experience shows that both BIC and AIC tend to choose the model with smallest K and no ad-hoc dependency. 
As an alternative, we choose a purely heuristic approach. 
Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest 20 eigenvalues of adjacency matrix X, which can tell us the numbers of communities embedded in network. 
Then, we record the rank of L and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data. \\

One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, where
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \frac{n(n-1)}{2},
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
\]

where $M$ is the current model,
$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
If rank$(L)=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1
\]
Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors. 
Additionally 1 in last is due to $\alpha$.
We want to find a M which minimizes BIC($M$) or AIC($M$) as a function of M. 
However these traditional methods seem to entail a serious problem. 
The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\hat{L}$,$\hat{S}$) with a pair of tuning parameters from given range of grid. 
We evaluate the model selected  
with following three evaluation metrics.
Table \ref{tab:table1}

\begin{figure}[h]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\hat{L}$ matrix. (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
\label{fig:figure1}
\end{figure}

\begin{table}[h]
\centering
\begin{tabular}{c|ccc|ccc|ccc}
   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10} 
   & SC        & AIC    & BIC    & SC        & AIC    & BIC    & SC        & AIC    & BIC   \\ \hline
M1 & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
M2 & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
M3 & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0    
\end{tabular}
\caption{}
\label{tab:table1}
\end{table}

\noindent \textbf{Community memberships of each nodes} Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$. 
We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors. 
Furthermore, we find one interesting phenomenon. 
Coordinates of each rows from first two eigenvectors of estimated $\hat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well. 
Our experience shows that with only first two eigenvectors of $\hat{L}$, we can also cluster the nodes comparably well. \\

\noindent \textbf{Ad-hoc links} Ad-hoc links of synthetic network data can be thought of as $"$across edges$"$ between clusters of nodes. 
Since indices of non-zero entries of $S$ are randomly chosen, there might be some indices of non-zero $S_{ij}$ entries where $L_{ij}$ is also non-zero. 
In this case, this makes the edges indistinguishable if they come from $S_{ij}$ or $L_{ij}$. 
Some of ``across edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$. 
So the total number of across edges might not be exactly same as we set in our data generation setting. \\

\noindent \textbf{Simulation Results} Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities. 
Also to see if it can separate the ad-hoc links from edges which come from common topics. 
Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$ respectively, give us the desirable results for 3 cases. 
Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph. 
However, we set the seeds in our simulation so that the results are reproducible. 
$Fig1$ shows us the result of clustered nodes using $k$-means algorithm on first $K(=rank(\hat{L}))$ eigenvectors. 
We plot the rows of first two eigenvectors on plane since it tends to visualize well the clustering behavior of nodes. 
Our model chooses well the ad-hoc links between clusters of nodes as can be verified in $Fig2$. 
We color the edges in blue whose corresponding elements of estimated $\hat{S}$ are non-zero, and black whose corresponding entries of $\hat{S}$ are zero.

\begin{figure}[b]
\begin{center}
\includegraphics[scale=0.75]{Fig2.pdf}
\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix. 
For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
\end{center}
\label{fig:figure2}
\end{figure}

@@

\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\hat{L}$ with rank 3, and $\hat{S}$ with $|supp(\hat{S})|=197$. 
We apply $k$-means algorithm on 3 eigenvectors of estimated $\hat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\hat{L}$ on plane in $Fig 4$. 
404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic. 
We list the first two topics discovered through our analysis. 
(Full lists of papers for each communities are provided in $\it https://sites.google.com/site/namjoonsuh/publications$)

\begin{itemize}
  \item "Variable selection (85 papers)"
  \item "Multiple Hypothesis Testing (54 papers)"
\end{itemize}

@@

\begin{figure}[b]
\includegraphics[width=1\textwidth]{Fig4.eps}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
\label{fig:figure4}
\end{figure}

\noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction". 
Due to small volume of each communities, we could check that false discoveries for each community are all zero.\\

\noindent Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics". 
Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics. 
Papers like "The Bayesian Lasso (T Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X Chen, et al. 2010)" are the examples of these papers. 
It is also interesting to think about a reason on papers which seem to have obvious membership in one of 5 communities other than Mixed topic classified as Mixed topic. 
For instance, "On the "degrees of freedom" on the LASSO (H Zou, et al. 2007)" is classified as Mixed Topic paper. 
We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities. 
Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics. \\

\noindent It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics". 
This is interesting since even though the dataset we consider is different from theirs, result is consistent. 
They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({\it i.e. each node is an author}). 
We consider the citation network of papers whose node degree is greater than or equal to 7.\\

\noindent\textbf{Ad-hoc links} Non-zero components of $\hat{S}$ capture the citation relationships among papers that are not attributable to the common topics. 
The model we select has 197 sparse edges (9\% of total edges), and all of them are positive edges. 
In Table 1, we provide 15 pairs of papers that have the most positive edges. 
All the 15 edges come from pairs of papers from different communities. 
For instance, the first pair of papers comes from Functional Analysis $(\it FuncAn)$ community and Variable selection $(\it VarSel)$ community. 
$\it FuncAn$ paper cites $\it VarSel$ paper for borrowing a mathematical representation to build a theorem. 
Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic. 
Second pair comes from $\it MulT$  and $\it VarSel$ community. 
$\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper. 
And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community. \\

\begin{figure}[!t]
\includegraphics[width=1\textwidth]{Fig3.eps}
\caption{Illustration of first two eigenvectors of estimated $\hat{L}$ matrix for original
citation network with 543 papers(left) and sub-network graph(right). Presentation
on clustering results of k-means algorithm with different colors.}
\label{fig:figure3}
\end{figure}

@@

Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
and (\ref{eq:1}). 
(\ref{eq:1}) sums over the all $(i,j)$ pairs. 
Due to the symmetry of $X$ and $\Theta=\alpha\mathbbm{1}\mathbbm{1}^T+L+S$, after scaling, the only difference lies in the inclusion of diagonal term of $\Theta$.
It should be noted that this slight modification neither leads to theoretical consequences nor noticeable difference in practice.
Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}. 
Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process. 
Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*},
\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
\hat{\Delta}^L = \hat{L}-L^{*},
\hat{\Delta}^S = \hat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$. 
We impose following assumptions for theoretical guarantees.

@@

With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem. 
In our result, we measure error using the squared Frobenius norm summed across both matrices:
\[
    e^{2}(\hat{\alpha}.\hat{L},\hat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\hat{L}\|_{F}^{2} + \|S^{*}-\hat{S}\|_{F}^{2}
\]

>>>>

\author[1]{Namjoon Suh*}
\author[1]{Xiaoming Huo}
\author[2]{Eric Heim}
\author[2]{Timothy Van Slyke}
\author[2]{Lee Seversky}

@@

\jnlcitation{\cname{%
\author{Suh Namjoon.},
\author{Xiaoming Huo},
\author{Eric Heim},
\author{Timothy Van Slyke}, and
\author{Lee Seversky}} (\cyear{2019}),
\ctitle{xxx}, \cjournal{journal.}, \cvol{2019;00:1--6}.}

@@

\footnotetext{\textbf{Abbreviations:} fused factor analysis and logistic graphical models, ADMM, network model}

@@

\item To ensure the separation of matrices $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that the eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad \mbox{where} \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T. 
\]
This condition uniquely identifies F up to a common orthogonal transformation of its columns.

@@

We propose a penalize likelihood estimation approach as follows:
\begin{eqnarray}
\label{eq:logistic10}
(\hat{\alpha}, \widehat{L}, \widehat{S})
= \mbox{arg min}_{\alpha, L, S} \left\{
-\frac{1}{n} \mathbb{L}_n(\alpha,  L, S; X) + \gamma \|S\|_1
+ \delta \|L\|_\ast\right\},
\end{eqnarray}
where $\gamma>0$ and $\delta>0$ are algorithmic parameters whose values will be discussed later,
the $L_1$ norm of matrix $S$ is defined as $\|S\|_1 = \sum_{i\neq j} S_{ij}$ (Note that we do not penalize the diagonal entries of $S$), and nuclear norm of matrix $L$ is defined as $\|L\|_\ast = {\mbox{trace}\sqrt{(L^T L)}}$.
Recall that both $S$ and $L$ are symmetric matrices.
The entries of matrix $S$ can either be positive or negative.
Note that we have imposed the diagonal entries of the matrix $X$ to be zeros.
Given that $L = F^T D F$ where matrix $D$ is diagonal with nonnegative diagonal entries, it is easy to see that matrix $L$ is positive semidefinite; which consequently leads to $\|L\|_\ast = \mbox{trace}(L)$, which is a linear functional to the matrix $L$.
The nuclear norm of $L$ penalizes the number of nonzero eigenvalues of $L$, which is the same as the rank
of $L$.
The regularization based on the nuclear norm was proposed in \cite{fazel2001rank}
and its statistical properties are studied in \cite{bach2008consistency}.

After we have obtained $\widehat{S}$ in \eqref{eq:logistic10}, we can uncover the graphical model by investigating non-zero entries in $\widehat{S}$.
On the other hand when we have calculated $\widehat{L}$, we may not be able to find binary matrix $F$ and nonnegative diagonal matrix $D$ such that $\widehat{L} = F^T D F.$
This is the price we have to pay for an amenable computational problem.
The rank of estimated $\widehat{L}$ will be our estimate of the number of factors (i.e., underlying common topics).
For the issue on assigning the community membership of each node $i$, we will discuss this later in Section 6.

@@

\subsection{Synthetic data}
\textbf{Data Generation}. 
Following the notation of our paper, each edge $X_{ij}$ follows Bernoulli distribution, whose parameter is parameterized by the probability, $P_{ij}=\frac{\exp (
\alpha+F_{i}^{T}DF_{j} +  S_{ij})}{1+\exp(\alpha+F_{i}^{T}DF_{j}+S_{ij})}$.
For sparse component $S$, we generate random numbers uniformly distributed over the indices of upper triangular part (off diagonal) of matrix $S$, and make it symmetry.
$F^{T}$ binary matrix has $\floor{\frac{n}{K}}$ ones in each columns, and has exactly one 1 in each rows.
We randomly choose one of rows, fill that row with ones, and project the column space of $F$ onto the orthogonal complement subspace of $\mathbbm{1}$ vector by multiplying the aforementioned $J = I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$ to $F$.
Diagonal elements of $D$ are generated from Unif$[7,8]$ (uniform distribution on $[7,8]$), and alpha is generated from Unif$[-3,-2]$.
We set $K=3,4,5$, $n=30,80,120$, and $nnz = 10, 20, 40$, where $nnz$ denotes number of non-zero component of the upper-triangular part of S.

\textbf{Choosing the tuning parameters}.
We have to admit the fact that choosing a good tuning parameter is an important but challenging issue in our problem.
In our problem where the observation can be seen as one realization of random graph, it is confusing whether to define the total number of observations as $N=\frac{n(n-1)}{2}$ or 1, since in usual BIC definition, we define effective sample size ``$n$,'' when we have $n$ i.i.d. observations.
Our experience shows that both BIC and AIC tend to choose the model with smallest $K$ and no ad-hoc dependency.
As an alternative, we choose a purely heuristic approach.
Following the Ji and Jin \cite{ji2016coauthorship}, we plot the largest $20$ eigenvalues of adjacency matrix $X$, which can tell us the numbers of communities embedded in network.
Then, we record the rank of $L$ and number of non-zero elements in S for each tuning parameter pair on grid, and choose proper pair of tuning parameters which can give us interesting interpretation of data.

One might wonder how traditional model selection methods, such as the Bayes Information Criterion (BIC;\cite{schwarz1978estimating}) or the AIC, where
\[
\mbox{BIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + |M| \log \frac{n(n-1)}{2},
\]
and
\[
\mbox{AIC}(M) = -2  \mathbb{L}_n( \hat{\beta}(M)) + 2|M|,
\]
where $M$ is the current model,
$\mathbb{L}_n( \hat{\beta}(M))$ is the maximal log-likelihood for a given model $M$,
and $|M|$ is the number of free parameters in $M$, which is determined by the number of non-zeros in $S$ and the low-rank matrix $L$.
If rank$(L)=K$, we can establish the following
\[
|M| = \sum_{i < j}1_{\{S_{ij} > 0\}} + n K - \frac{K(K-1)}{2} + 1
\]
Because the number of free parameters in $L$ is $K$ plus $nk - K(K+1)/2$, which is the number of free parameters in determining $K$ orth-normal vectors.
Additionally $1$ in the last is due to $\alpha$.
We want to find an $M$ which minimizes BIC($M$) or AIC($M$) as a function of M.
However these traditional methods seem to entail a serious problem.
The assumptions used to derive BIC or AIC are not satisfied here, since each edges in a graph are not identically distributed.
Our experience shows that both BIC and AIC tend to choose the most parsimonious model with the smallest K and no ad-hoc dependency among all the estimated ($\widehat{L}$,$\widehat{S}$) with a pair of tuning parameters from given range of grid.
We evaluate the model selected
with following three evaluation metrics.
Table \ref{tab:table1}

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\widehat{L}$ matrix. (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
\label{fig:figure1}
\end{figure}

\begin{table}[h]
\centering
\begin{tabular}{c|ccc|ccc|ccc}
   & \multicolumn{3}{c|}{Case 1} & \multicolumn{3}{c|}{Case 2} & \multicolumn{3}{c}{Case 3} \\ \cline{2-10}
   & SC        & AIC    & BIC    & SC        & AIC    & BIC    & SC        & AIC    & BIC   \\ \hline
M1 & 1         & 0      & 0      & 1         & 0      & 0      & 1         & 0      & 0     \\
M2 & 0.5       & 0      & 0      & 0.842     & 0      & 0      & 0.725     & 0      & 0     \\
M3 & 0.007     & 0      & 0      & 0.008     & 0      & 0      & 0.0113    & 0      & 0
\end{tabular}
\caption{xxx}
\label{tab:table1}
\end{table}

\textbf{Community memberships of each nodes}. 
Given a network data, after fitting the model with a proper pair of tuning parameters, $(\gamma,\delta)$, we need to determine whether node $i$ belongs to topic $k$.
We applied a simple $k$-means clustering on the fitted $L$ matrix's first $K$ eigenvectors.
Furthermore, we find one interesting phenomenon.
Coordinates of each rows from first two eigenvectors of estimated $\widehat{L}$ matrix in our model characterize the clustering behavior of embedded topics reasonably well.
Our experience shows that with only first two eigenvectors of $\widehat{L}$, we can also cluster the nodes comparably well.

\textbf{Ad-hoc links}. 
Ad-hoc links of synthetic network data can be thought of as ``across edges'' between clusters of nodes.
Since indices of non-zero entries of $S$ are randomly chosen, there might be some indices of non-zero $S_{ij}$ entries where $L_{ij}$ is also non-zero.
In this case, this makes the edges indistinguishable if they come from $S_{ij}$ or $L_{ij}$.
Some of ``across edges" are also attributed to $\alpha$, and unfortunately, our algorithm cannot make a difference whether the edge comes from $\alpha$ or $S_{ij}$.
So the total number of across edges might not be exactly same as we set in our data generation setting.

\textbf{Simulation Results}. 
Our goal in this simulation experiment is to check if our model can cluster each nodes into correct communities.
Also to see if it can separate the ad-hoc links from edges which come from common topics.
Tuning parameter pairs, $(\gamma,\delta) = (0.01,0.03),(0.004,0.014),(0.003,0.013)$, respectively, give us the desirable results for the three cases.
Note that different dynamics of network requires different choices of tuning parameters even the synthetic setting is same, since we are generating the random graph.
However, we set the seeds in our simulation so that the results are reproducible.
Fig. \ref{fig:figure1} shows us the result of clustered nodes using the $k$-means algorithm on the first $K(=\mbox{rank}(\widehat{L}))$ eigenvectors.
We plot the rows of first two eigenvectors on the cartesian plane since it visualizes well the clustering behavior of the nodes.
Our model chooses well the ad-hoc links between clusters of nodes as can be verified in Fig. \ref{fig:figure2}.
We color the edges in blue whose corresponding elements of estimated $\widehat{S}$ are non-zero, and black whose corresponding entries of $\widehat{S}$ are zero.

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.75]{Fig2.pdf}
\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\widehat{S}$ matrix.
For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
\label{fig:figure2}
\end{center}
\end{figure}

@@

\noindent $(\gamma,\delta) = (0.000912,0.0097)$ gives us $\widehat{L}$ with rank 3, and $\widehat{S}$ with $|supp(\widehat{S})|=197$.
We apply $k$-means algorithm on 3 eigenvectors of estimated $\widehat{L}$ matrix, and visualize the result of clustering by plotting the rows of first two eigenvectors of $\widehat{L}$ on plane in $Fig 4$xxxx.
404 papers colored in green are densely clustered nearby the origin with a short tail, $(Fig 4)$, and $k$-means classifies these papers as third topic.
We list the first two topics discovered through our analysis.
(Full lists of papers for each communities are provided in $\it https://sites.google.com/site/namjoonsuh/publications$)

\begin{itemize}
  \item "Variable selection (85 papers)" xxxxx
  \item "Multiple Hypothesis Testing (54 papers)"
\end{itemize}

@@

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig4.eps}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
\label{fig:figure4}
\end{figure}

Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction".
Due to small volume of each communities, we could check that false discoveries for each community are all zero.

Sub-network structure has also a big chunk of papers which we refer to as "Mixed Topics".
Not only could we see the papers with topics on "Learning Theory", "Non-parametric/semi-parametric statistics", "Spatial Statistics", "Theoretical Machine Learning", which does not seem to belong to any of five communities listed above, but also we could identify the papers with combinations of two or three topics.
Papers like "The Bayesian Lasso (T. Park, et al. 2008)", "Coordinate-independent sparse sufficient dimension reduction and variable selection (X. Chen, et al. 2010)" are the examples of these papers.
It is also interesting to think about a reason on papers which seem to have obvious membership in one of $5$ communities other than Mixed topic classified as Mixed topic.
For instance, "On the "degrees of freedom" on the LASSO (H. Zou, et al. 2007)" is classified as Mixed Topic paper.
We can simply guess model selection has lots of applications in other topics, so it might cite or have been cited by many papers in other communities.
Actually, out of 19 citation relationships it has with other papers, 12 of them came from the relationships with papers from Mixed topics.

It is worth to note that our result is consistent with that from Ji and Jin in a sense that they also recover "Multiple Testing", "Variable selection" and "non-parametric Bayesian statistics".
This is interesting since even though the dataset we consider is different from theirs, result is consistent.
They focus their attentions on analyzing {\it "weakly connected giant component"} for a citation network of each paper's authors ({i.e., each node is an author}).
We consider the citation network of papers whose node degree is greater than or equal to 7.

\textbf{Ad-hoc links}. 
Non-zero components of $\widehat{S}$ capture the citation relationships among papers that are not attributable to the common topics.
The model we select has 197 sparse edges (9\% of total edges), and all of them are positive edges.
In Table 1, we provide 15 pairs of papers that have the most positive edges.
All the 15 edges come from pairs of papers from different communities.
For instance, the first pair of papers comes from the Functional Analysis community (denoted by \emph{FuncAn}) and Variable selection $(\it VarSel)$ community. xxxx 
$\it FuncAn$ paper cites $\it VarSel$ paper for borrowing a mathematical representation to build a theorem.
Though it might seem to be a crucial step for building a theorem in their paper, we cannot say that two papers are closely related in terms of topic.
Second pair comes from $\it MulT$  and $\it VarSel$ community.
$\it MulT$ paper briefly mention about $\it VarSel$ paper in future work section, suggesting a possible way of combining their work and work in $\it VarSel$ paper.
And we also observe that as the weight of edges decreases, increasing number of pairs of papers both come from "Mixed topics" community.

\begin{figure}[htbp]
\includegraphics[width=1\textwidth]{Fig3.eps}
\caption{Illustration of first two eigenvectors of estimated $\widehat{L}$ matrix for original
citation network with 543 papers(left) and sub-network graph(right). Presentation
on clustering results of k-means algorithm with different colors.}
\label{fig:figure3}
\end{figure}

@@

Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
and (\ref{eq:1}).
(\ref{eq:1}) sums over the all $(i,j)$ pairs.
Due to the symmetry of $X$ and $\Theta=\alpha\mathbbm{1}\mathbbm{1}^T+L+S$, after scaling, the only difference lies in the inclusion of diagonal term of $\Theta$.
It should be noted that this slight modification neither leads to theoretical consequences nor noticeable difference in practice.
Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}.
Let ($\hat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process.
Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*},
\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
\hat{\Delta}^L = \widehat{L}-L^{*},
\hat{\Delta}^S = \widehat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
We impose following assumptions for theoretical guarantees.

@@

With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem.
In our result, we measure error using the squared Frobenius norm summed across both matrices:
\[
    e^{2}(\hat{\alpha}.\widehat{L},\widehat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\widehat{L}\|_{F}^{2} + \|S^{*}-\widehat{S}\|_{F}^{2}
\]

\begin{theorem}
Under the assumptions (4.1) and (4.2),
if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying
\begin{align}
\delta \geq 4\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 4\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
\end{align}
There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\widehat{L},\widehat{S})$
\begin{align}
    e^{2}(\hat{\alpha},\widehat{L},\widehat{S}) \leq
    c_{1}\frac{\delta^{2}}{\tau^{2}} +
    c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\} +
    c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\|S^*_{M^\perp}\|_{1}\bigg\}
\end{align}
\end{theorem}
